\section{Structure}
\subsection{Folder structure}
The source code is located in the \verb|src| directory. 
This directory contains 3 subdirectories. 
The first one contains the code required to create the desktop app. 
The second one contains the code required to create the website 
and the last one contains the htaccess file that is required when we upload the files on a web server.

\subsubsection{Desktop app}
The directory \verb|src/eslintme-native-wrapper| contains 
the source code for the desktop app. 

\begin{itemize}
    \item \verb|index.js| is the entry point of the electron app.
    \item \verb|preload.js| is the bridge between the electron app and the website.
    \item \verb|package.json| contains meta data related to the app and scripts to run and build the app.
\end{itemize}

\subsubsection{Website}
The directory \verb|src/eslintme-website| contains 
the source code for the website.
\subsubsection{Htaccess}
The directory \verb|src/htaccess| contains a file named \verb|.htaccess| that 
describes how Apache should rewrite some requests. 
This allows the next.js app to work properly even if the page is reloaded. 

\noindent Note: .htaccess files only work in Apache, 
you may want to adapt this solution to the server you are using.

\subsubsection{Core}
The directory \verb|lib/eslintme-core| located in \verb|src/eslintme-website| contains 
the source code for the "business logic" of the app. This would allow an other developer to create a different GUI but keep the logic behind ESLintME

\subsection{Communications inside the software}
The different parts of the software communicate with each other thanks to special events that are described in the "Events" section.

\noindent The components can interact with each other using the \texttt{\href{https://developer.mozilla.org/fr/docs/Web/API/Window/postMessage}{postMessage}} method.

\noindent The worker and the components that use it can communicate though the mechanisms provided by the 
\texttt{\href{https://developer.mozilla.org/fr/docs/Web/API/Web_Workers_API/Using_web_workers}{Web Workers API}}.